---
title: "Technical Analysis"
author: "Allen Wang"
date: "2023-02-13"
output: 
  tufte::tufte_handout: default
---

# Overview
In this report, I will analyze ten different stocks by exploring different technical indicators. Technical indicators are patterns from data that can be used to predict future pricing of assets and make decisions about trades.
First, I will compute these indicators and discuss their impact within the context of these ten stocks.
Next, I will visualize these indicators and explore trends and opportunities.


# Dataset overview
In this dataset, I will be analyzing ten stocks:
598 entries each
26 entries per day
23 days total

* FAST (Fastenal)
* WBA (Walgreens)
* AAPL (Apple)
* MS (Morgan Stanley)
* CVX (Chevron)
* JPM (JP Morgan)
* XOM (Exxon Mobil) 3589 - 4186
* TSLA (Tesla) 4188 - 4784
* JD (JD.com) 4785 - 5382 (Chinese stock)
* SPCE (Virgin Galactic)





```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(PerformanceAnalytics)
library(zoo)
library(ggplot2)
library(quantmod)
library(tidyr)
library(reshape2)  
library(pracma)
library(TTR)
library(patchwork)
library(tidyquant)
```



```{r, include = FALSE}
df <- read.csv("/Users/allenwang/Desktop/junior/Project/TradingIntern.WS.data.csv")
```

```{r, echo = FALSE}
fast <- df[1:598, ]
wba <- df[599:1196, ]
aapl <- df[1197:1794, ]
ms <- df[1795:2392, ]
cvx <- df[2393:2990, ]
jpm <- df[2991:3588, ]
xom <- df[3589:4186, ]
tsla <- df[4187:4784, ]
jd <- df[4785:5382, ]
spce <- df[5383:5980, ]
```




```{r, include = FALSE}
symbols <- c("fast", "wba", "aapl", "ms", "cvx", "jpm", "xom", "tsla", "jd", "spce" )
```


# Price overview

```{r, echo = FALSE}
# Extract price data for each stock
aapl_price <- aapl$midpoint
cvx_price <- cvx$midpoint
fast_price <- fast$midpoint
jd_price <- jd$midpoint
jpm_price <- jpm$midpoint
ms_price <- ms$midpoint
spce_price <- spce$midpoint
tsla_price <- tsla$midpoint
wba_price <- wba$midpoint
xom_price <- xom$midpoint
```


```{r, echo = FALSE}
# Plot each stock price over time
aapl_chart <- ggplot(data=aapl, aes(x=X, y=midpoint, group=1)) +
  geom_line() + 
  labs(title = "Apple Stock Price (March 2022)") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Price ($)")

cvx_chart <- ggplot(data=cvx, aes(x=X, y=midpoint, group=1)) +
  geom_line() + 
  labs(title = "Chevron Stock Price (March 2022)") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Price ($)")

fast_chart <- ggplot(data=fast, aes(x=X, y=midpoint, group=1)) +
  geom_line() + 
  labs(title = "Fastenal Stock Price (March 2022)") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Price ($)")

jd_chart <- ggplot(data=jd, aes(x=X, y=midpoint, group=1)) +
  geom_line() + 
  labs(title = "JD.com Stock Price (March 2022)") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Price ($)")

jpm_chart <- ggplot(data=jpm, aes(x=X, y=midpoint, group=1)) +
  geom_line() + 
  labs(title = "JP Morgan Stock Price (March 2022)") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Price ($)")

ms_chart <- ggplot(data=ms, aes(x=X, y=midpoint, group=1)) +
  geom_line() + 
  labs(title = "Morgan Stanley Stock Price (March 2022)") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Price ($)")

spce_chart <- ggplot(data=spce, aes(x=X, y=midpoint, group=1)) +
  geom_line() + 
  labs(title = "Virgin Galactic Stock Price (March 2022)") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Price ($)")

tsla_chart <- ggplot(data=tsla, aes(x=X, y=midpoint, group=1)) +
  geom_line() + 
  labs(title = "Tesla Stock Price (March 2022)") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Price ($)")

wba_chart <- ggplot(data=wba, aes(x=X, y=midpoint, group=1)) +
  geom_line() + 
  labs(title = "Walgreens Stock Price (March 2022)") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Price ($)")

xom_chart <- ggplot(data=xom, aes(x=X, y=midpoint, group=1)) +
  geom_line() + 
  labs(title = "Exxon Mobil Stock Price (March 2022)") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Price ($)")

```


```{r, echo = FALSE}
aapl_chart

cvx_chart

fast_chart

jd_chart

jpm_chart

ms_chart

spce_chart

tsla_chart

wba_chart

xom_chart

```

```{r}
fast$vol_ma <- movavg(fast$volume, 130, type = "e")
```

```{r, echo = FALSE, warning = FALSE}
fast_vol <- ggplot(data = fast, aes(x = X)) + 
  geom_bar(aes(y = volume), stat="identity", linewidth=.1, color = "blue", alpha=.4) +
  geom_line(aes(y = vol_ma), color = "red") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Volume") +
  labs(title = "Fastenal Volume")
```


```{r, echo = FALSE, warning = FALSE}
fast_vol
```

```{r}
volume_plot <- function(data) {
  data$vol_ma <- movavg(data$volume, 52, type = "e")
  
  p <- ggplot(data = data, aes(x = X)) + 
    geom_bar(aes(y = volume), stat="identity", linewidth=.1, color = "blue", alpha=.4) +
    geom_line(aes(y = vol_ma), color = "red") +
    scale_x_continuous(name = "Time") +
    scale_y_continuous(name = "Volume") +
    labs(title = "Volume")
    
  return(p)
}
```





```{r}
fast$vol_ma <- movavg(fast$volume, 130, type = "e")
```

```{r, echo = FALSE, warning = FALSE}
fast_vol <- ggplot(data = fast, aes(x = X)) + 
  geom_bar(aes(y = volume), stat="identity", linewidth=.1, color = "blue", alpha=.4) +
  geom_line(aes(y = vol_ma), color = "red") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Volume") +
  labs(title = "Volume")
```


```{r, echo = FALSE, warning = FALSE}
fast_vol
```


```{r}
volume_plot(wba)
```


c("fast", "wba", "aapl", "ms", "cvx", "jpm", "xom", "tsla", "jd", "spce" )
```{r}
volume_plot(fast)
```

```{r}
volume_plot(wba)
```

```{r}
volume_plot(aapl)
```

```{r}
volume_plot(ms)
```

```{r}
volume_plot(cvx)
```

```{r}
volume_plot(jpm)
```

```{r}
volume_plot(xom)
```

```{r}
volume_plot(tsla)
```

```{r}
volume_plot(jd)
```

```{r}
volume_plot(spce)
```

# Closing Prices
```{r, include = FALSE}
  # Extract closing prices
  data$closing <- data[seq(0, nrow(df), 26), ]
  data$closing <- na.omit(data$closing)
```



# Technical Indicators
I will explore these ___ indicators:

* Simple moving average (SMA)
* Exponential weighted moving average (EWMA)
* Bollinger Bands (BB)
* Relative strength index (RSI)
* Moving average convergence divergence (MACD)
* Money flow index
* Force index
* Ease of movement


# Simple Moving Average (SMA)
The simple moving average can be used to find support and resistance

```{r, echo = FALSE}
sma_plot <- function(data) {
  data$ma_daily <- movavg(data$midpoint, 26, type = "s")
  data$ma_twoday <- movavg(data$midpoint, 52, type = "s")
  data$ma_weekly <- movavg(data$midpoint, 130, type = "s")
  
  
  p <- ggplot(data = data, aes(x = X)) + 
    
    geom_line(aes(y = midpoint), color = "steelblue") +
    geom_line(aes(y = ma_daily), color = "orange") +
    geom_line(aes(y = ma_twoday), color = "red") +
    geom_line(aes(y = ma_weekly), color = "black") + 
    labs(title = "Moving Averages (March 2022)") +
    scale_x_continuous(name = "Time") +
    scale_y_continuous(name = "Price ($)")
  
  return(p)
}
```

## Fastenal
```{r, echo = FALSE}
sma_plot(fast)
```

## Walgreens
```{r}
sma_plot(wba)
```

## Apple
```{r}
sma_plot(aapl)
```

## Morgan Stanley
```{r}
sma_plot(ms)
```

## Chevron
```{r}
sma_plot(cvx)
```

## JP Morgan
```{r}
sma_plot(jpm)
```

## Exxon Mobil
```{r}
sma_plot(xom)
```

## Tesla
```{r}
sma_plot(tsla)
```

## JD.com
```{r}
sma_plot(jd)
```



Analysis: The graph of moving averages for Fastenal seems to indicate a golden cross pattern in which the short-term moving average crosses above the longer-term moving averages. This points towards a major rally.


Analysis: The graph of Walgreen stock shows the opposite: a death cross, in which there seems to be a major downturn since the short term moving average has crossed below the longer term average.



Analysis: This graph shows a dip and recovery in Apple's stock price over March 2022. Note that the crossing of the indicators after the price started recovering.




# Bollinger Bands (BB)
Bollinger bands consist of the middle band (SMA) and the upper and lower bands, which are 2 standard deviations above and below the SMA, respectively.

```{r, echo = FALSE}
bb_plot <- function(data) {
  # Calculate one standard deviation of differences between current price and daily moving average
  data$sd <- sd(data$midpoint - data$ma_daily)
  # Calculate upper and lower Bollinger bands
  data$upperBB <- data$ma_daily + 2 * data$sd
  data$lowerBB <- data$ma_daily - 2 * data$sd
  
  
  p <- ggplot(data = data, aes(x = X)) + 
    geom_line(aes(y = upperBB), color = "blue") +
    geom_line(aes(y = ma_daily), color = "black") +
    
    geom_line(aes(y = midpoint), color = "steelblue") +
    geom_line(aes(y = lowerBB), color = "red") +
    scale_x_continuous(name = "Time") +
    scale_y_continuous(name = "Price ($)") + labs(title = "Bollinger Bands")
  
  return(p)
}
```

## Fastenal
```{r, echo = FALSE}
bb_plot(fast)
```

## Walgreens
```{r, echo = FALSE}
bb_plot(wba)
```

## Apple
```{r, echo = FALSE}
bb_plot(aapl)
```

## Morgan Stanley
```{r, echo = FALSE}
bb_plot(ms)
```

## Chevron
```{r, echo = FALSE}
bb_plot(cvx)
```

## JP Morgan
```{r, echo = FALSE}
bb_plot(jpm)
```

## Exxon Mobil
```{r, echo = FALSE}
bb_plot(xom)
```

## Tesla
```{r, echo = FALSE}
bb_plot(tsla)
```

## JD.com
```{r, echo = FALSE}
bb_plot(jd)
```

## Virgin Galactic
```{r, echo = FALSE}
bb_plot(spce)
```






Analysis: Fastenal's stock price over March 2022 displays "three pushes to high", with the first push occuring around time 130, the second around 390, and the last around 600. This indicates decreasing momentum and volume.


Analysis: This chart of Bollinger bands for Walgreens seems to show the middle of a double bottom, where the price fell then rose then fell again, indicating a good time to buy since the stock is preparing for an uptrend.



Analysis:





Analysis: Looking at a chart of US retail gas prices, the price for gasoline increased from 3.70 per gallon on March 1 to 4.40 per gallon on March 14 then down to 4.27 per gallon at the end of the month. The moving averages/Bollinger bands seem to mirror this pattern almost exactly.



Analysis: Wide Bollinger bands indicate high volatility.


Analysis: Seems to be M-shaped, kind of the same as the one for Chevron. Looking at a chart of US retail gas prices, the price for gasoline increased from 3.70 per gallon on March 1 to 4.40 per gallon on March 14 then down to 4.27 per gallon at the end of the month. The moving averages/Bollinger bands seem to mirror this pattern almost exactly.








Analysis: Virgin Galactic 



# Exponential Weighted Moving Average (EWMA)
The exponential weighted moving average is used as a measure of volatility through historical predictions from past pricing data and implied predictions from market conditions.



## Fastenal EWMA
```{r, echo = FALSE}
fast$ewma <- movavg(fast_price, 26, type = "e")
```

## Walgreens EWMA
```{r, echo = FALSE}
wba$ewma <- movavg(wba_price, 26, type = "e")
```

## Apple EWMA
```{r, echo = FALSE}
aapl$ewma <- movavg(aapl_price, 26, type = "e")
```

## Morgan Stanley EWMA
```{r, echo = FALSE}
ms$ewma <- movavg(ms_price, 26, type = "e")
```

## Chevron EWMA
```{r, echo = FALSE}
cvx$ewma <- movavg(cvx_price, 26, type = "e")
```

## JP Morgan EWMA
```{r, echo = FALSE}
jpm$ewma <- movavg(jpm_price, 26, type = "e")
```

## Exxon Mobil EWMA
```{r, echo = FALSE}
xom$ewma <- movavg(xom_price, 26, type = "e")
```

## Tesla EWMA
```{r, echo = FALSE}
tsla$ewma <- movavg(tsla_price, 26, type = "e")
```

## JD.com EWMA
```{r, echo = FALSE}
jd$ewma <- movavg(jd_price, 26, type = "e")
```

## Virgin Galactic EWMA
```{r, echo = FALSE}
spce$ewma <- movavg(spce_price, 26, type = "e")
```



# Relative Strength Index (RSI)
Relative strength index is used to determine momentum of an asset to describe the speed of price changes. Assets are overbought when RSI > 70 and oversold when RSI < 30.

```{r}
rsi_plot <- function(data) {
  # Calculate relative strength index
  data$rsi <- RSI(data$midpoint, n = 26)
  
  p <- ggplot(data = data, aes(x = X)) + 
    geom_line(aes(y = ma_daily), color = "black") +
    geom_line(aes(y = rsi), color = "orange") + 
    labs(title = "Relative Strength Index (March 2022)") +
    scale_y_continuous(name = "Price ($)", breaks = c(30, 50, 70), limits = c(20,80)) + 
    scale_x_continuous(name = "Time")
  
  return(p)
}
```


## Fastenal 
```{r, echo = FALSE, warning = FALSE}
rsi_plot(fast)
```


## Walgreens
```{r, echo = FALSE, warning = FALSE}
rsi_plot(wba)
```

## Apple
```{r, echo = FALSE, warning = FALSE}
rsi_plot(aapl)
```

## Morgan Stanley
```{r, echo = FALSE, warning = FALSE}
rsi_plot(ms)
```

## Chevron
```{r, echo = FALSE, warning = FALSE}
rsi_plot(cvx)
```

## JP Morgan
```{r, echo = FALSE, warning = FALSE}
rsi_plot(jpm)
```

## Exxon Mobil
```{r, echo = FALSE, warning = FALSE}
rsi_plot(xom)
```

## Tesla
```{r, echo = FALSE, warning = FALSE}
rsi_plot(tsla)
```

## JD.com
```{r, echo = FALSE, warning = FALSE}
rsi_plot(jd)
```

## Virgin Galactic
```{r, echo = FALSE, warning = FALSE}
rsi_plot(spce)
```


# Moving Average Convergence/Divergence

```{r}
macd_plot <- function(data) {
  
  # Calculate the exponential moving average
  data$macdLine <- data$ma_daily - data$ma_twoday
  
  # Calculate the signal line
  data$signalLine <- movavg(data$macdLine, 9, type = "e")
  
  # Calculate the histogram
  data$histogram <- data$macdLine - data$signalLine
  
  p <- ggplot(data = data, aes(x = X)) + 
    geom_bar(aes(y = histogram), stat="identity", linewidth=.1, color = "blue", alpha=.4) +
    geom_line(aes(y = signalLine), color = "red", linetype = "dashed") +
    geom_line(aes(y = macdLine), color = "steelblue") +
    scale_x_continuous(name = "Time") +
    scale_y_continuous(name = "MACD") +
    labs(title = "Moving Average Convergence/Divergence (March 2022)")
  
  return(p)
}
```

## Fastenal
```{r, echo = FALSE, warning = FALSE}
macd_plot(fast)
```

## Walgreens
```{r, echo = FALSE, warning = FALSE}
macd_plot(wba)
```

## Apple
```{r, echo = FALSE, warning = FALSE}
macd_plot(aapl)
```

## Morgan Stanley
```{r, echo = FALSE, warning = FALSE}
macd_plot(ms)
```

## Chevron
```{r, echo = FALSE, warning = FALSE}
macd_plot(cvx)
```

## JP Morgan
```{r, echo = FALSE, warning = FALSE}
macd_plot(jpm)
```

## Exxon Mobil
```{r, echo = FALSE, warning = FALSE}
macd_plot(xom)
```

## Tesla
```{r, echo = FALSE, warning = FALSE}
macd_plot(tsla)
```

## JD.com
```{r, echo = FALSE, warning = FALSE}
macd_plot(jd)
```

## Virgin Galactic
```{r, echo = FALSE, warning = FALSE}
macd_plot(spce)
```



Analysis: Fastenal seems to be overbought or oversold and will return to normal levels since there are multiple crossover points for the two moving averages that are decreasing in magnitude.




# On-balance volume
```{r}
obv_plot <- function(data) {
  data$obv <- OBV(data$midpoint, data$volume)
  data$obv_ma <- movavg(data$obv, 52, type = "e")
  
  p <- ggplot(data = data, aes(x = X)) + 
    geom_bar(aes(y = obv), stat="identity", linewidth=.1, color = "blue", alpha=.4) +
    geom_line(aes(y = obv_ma), color = "red") +
    scale_x_continuous(name = "Time") +
    scale_y_continuous(name = "On Balance Volume") +
    labs(title = "Volume")
    
  return(p)
}
```

## Fastenal
```{r}
obv_plot <- function(data) {
  data$obv <- OBV(data$midpoint, data$volume)
  data$obv_ma <- movavg(data$obv, 52, type = "e")
  
  p <- ggplot(data = data, aes(x = X)) + 
    geom_bar(aes(y = obv), stat="identity", linewidth=.1, color = "blue", alpha=.4) +
    geom_line(aes(y = obv_ma), color = "red") +
    scale_x_continuous(name = "Time") +
    scale_y_continuous(name = "On Balance Volume") +
    labs(title = "Volume")
    
  return(p)
}
```
## Fastenal
```{r}
obv_plot(fast)
```

## Walgreens
```{r}
obv_plot(wba)
```

## Apple
```{r}
obv_plot(aapl)
```

## Morgan Stanley
```{r}
obv_plot(ms)
```

## Chevron
```{r}
obv_plot(cvx)
```

## JP Morgan
```{r}
obv_plot(jpm)
```

## Exxon Mobil
```{r}
obv_plot(xom)
```

## Tesla
```{r}
obv_plot(tsla)
```

## JD.com
```{r}
obv_plot(jd)
```




# Ease of movement

```{r}
eom_plot <- function(data) {
  # Calculate ease of movement
  data$eom <- EMV(HL = data$midpoint, n = 26)
  data$eom_ma <- movavg(data$eom, 26, type = "e")
  
  p <- ggplot(data = data, aes(x = X)) + 
    geom_bar(aes(y = eom), stat="identity", linewidth=.1, color = "blue", alpha=.4) +
    geom_line(aes(y = eom_ma), color = "black") +
    scale_x_continuous(name = "Time") +
    scale_y_continuous(name = "Ease of Movement") +
    labs(title = "Ease of Movement")
    
  return(p)
}
```



## Fastenal
```{r, echo = FALSE, warning = FALSE}
obv_plot(fast)
```

## Walgreens
```{r, echo = FALSE, warning = FALSE}
obv_plot(wba)
```

## Apple
```{r, echo = FALSE, warning = FALSE}
obv_plot(aapl)
```

## Morgan Stanley
```{r, echo = FALSE, warning = FALSE}
obv_plot(ms)
```

## Chevron
```{r, echo = FALSE, warning = FALSE}
obv_plot(cvx)
```

## JP Morgan
```{r, echo = FALSE, warning = FALSE}
obv_plot(jpm)
```

## Exxon Mobil
```{r, echo = FALSE, warning = FALSE}
obv_plot(xom)
```

## Tesla
```{r, echo = FALSE, warning = FALSE}
obv_plot(tsla)
```

## JD.com
```{r, echo = FALSE, warning = FALSE}
obv_plot(jd)
```

## Virgin Galactic
```{r, echo = FALSE, warning = FALSE}
obv_plot(spce)
```




# Force index 
```{r}

```





## Fastenal
```{r, echo = FALSE, warning = FALSE}
obv_plot(fast)
```

## Walgreens
```{r, echo = FALSE, warning = FALSE}
obv_plot(wba)
```

## Apple
```{r, echo = FALSE, warning = FALSE}
obv_plot(aapl)
```

## Morgan Stanley
```{r, echo = FALSE, warning = FALSE}
obv_plot(ms)
```

## Chevron
```{r, echo = FALSE, warning = FALSE}
obv_plot(cvx)
```

## JP Morgan
```{r, echo = FALSE, warning = FALSE}
obv_plot(jpm)
```

## Exxon Mobil
```{r, echo = FALSE, warning = FALSE}
obv_plot(xom)
```

## Tesla
```{r, echo = FALSE, warning = FALSE}
obv_plot(tsla)
```

## JD.com
```{r, echo = FALSE, warning = FALSE}
obv_plot(jd)
```

## Virgin Galactic
```{r, echo = FALSE, warning = FALSE}
obv_plot(spce)
```

# Money flow index
## Fastenal
```{r, echo = FALSE, warning = FALSE}
obv_plot(fast)
```

## Walgreens
```{r, echo = FALSE, warning = FALSE}
obv_plot(wba)
```

## Apple
```{r, echo = FALSE, warning = FALSE}
obv_plot(aapl)
```

## Morgan Stanley
```{r, echo = FALSE, warning = FALSE}
obv_plot(ms)
```

## Chevron
```{r, echo = FALSE, warning = FALSE}
obv_plot(cvx)
```

## JP Morgan
```{r, echo = FALSE, warning = FALSE}
obv_plot(jpm)
```

## Exxon Mobil
```{r, echo = FALSE, warning = FALSE}
obv_plot(xom)
```

## Tesla
```{r, echo = FALSE, warning = FALSE}
obv_plot(tsla)
```

## JD.com
```{r, echo = FALSE, warning = FALSE}
obv_plot(jd)
```

## Virgin Galactic
```{r, echo = FALSE, warning = FALSE}
obv_plot(spce)
```
# Ease of movement









## Fastenal
```{r, echo = FALSE, warning = FALSE}
obv_plot(fast)
```

## Walgreens
```{r, echo = FALSE, warning = FALSE}
obv_plot(wba)
```

## Apple
```{r, echo = FALSE, warning = FALSE}
obv_plot(aapl)
```

## Morgan Stanley
```{r, echo = FALSE, warning = FALSE}
obv_plot(ms)
```

## Chevron
```{r, echo = FALSE, warning = FALSE}
obv_plot(cvx)
```

## JP Morgan
```{r, echo = FALSE, warning = FALSE}
obv_plot(jpm)
```

## Exxon Mobil
```{r, echo = FALSE, warning = FALSE}
obv_plot(xom)
```

## Tesla
```{r, echo = FALSE, warning = FALSE}
obv_plot(tsla)
```

## JD.com
```{r, echo = FALSE, warning = FALSE}
obv_plot(jd)
```

## Virgin Galactic
```{r, echo = FALSE, warning = FALSE}
obv_plot(spce)
```

