---
title: "Voleon Work Sample"
author: "Allen Wang"
date: "2023-02-13"
output: 
  tufte::tufte_handout: default
---

# Overview
In this report, I will analyze ten different stocks by exploring different technical indicators. Technical indicators are patterns from data that can be used to predict future pricing of assets and make decisions about trades.
First, I will compute these indicators and discuss their impact within the context of these ten stocks.
Next, I will visualize these indicators and explore trends and opportunities.


# Dataset overview
In this data set, I will be analyzing ten stocks:

* FAST (Fastenal)
* WBA (Walgreens)
* AAPL (Apple)
* MS (Morgan Stanley)
* CVX (Chevron)
* JPM (JP Morgan)
* XOM (Exxon Mobil)
* TSLA (Tesla)
* JD (JD.com)
* SPCE (Virgin Galactic)

There are 598 entries each, consisting of 26 entries per day and 23 days total




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(PerformanceAnalytics)
library(zoo)
library(ggplot2)
library(quantmod)
library(tidyr)
library(reshape2)  
library(pracma)
library(TTR)
library(patchwork)
library(tidyquant)
library(RcppRoll)
library(mefa)
```



```{r, include = FALSE}
df <- read.csv("/Users/allenwang/Desktop/junior/Project/TradingIntern.WS.data.csv")
```


```{r, echo = FALSE}
df$datetime <- as.POSIXct(df$datetime, format = "%Y-%m-%d %H:%M:%S")
```

```{r, echo = FALSE, include = FALSE}
summary(df)
```



```{r, echo = FALSE}
fast <- df[1:598, ]
wba <- df[599:1196, ]
aapl <- df[1197:1794, ]
ms <- df[1795:2392, ]
cvx <- df[2393:2990, ]
jpm <- df[2991:3588, ]
xom <- df[3589:4186, ]
tsla <- df[4187:4784, ]
jd <- df[4785:5382, ]
spce <- df[5383:5980, ]
```




```{r, include = FALSE}
symbols <- c("fast", "wba", "aapl", "ms", "cvx", "jpm", "xom", "tsla", "jd", "spce" )
```

\newpage

# Price overview

```{r, echo = FALSE}
# Extract price data for each stock
aapl_price <- aapl$midpoint
cvx_price <- cvx$midpoint
fast_price <- fast$midpoint
jd_price <- jd$midpoint
jpm_price <- jpm$midpoint
ms_price <- ms$midpoint
spce_price <- spce$midpoint
tsla_price <- tsla$midpoint
wba_price <- wba$midpoint
xom_price <- xom$midpoint
```


```{r, echo = FALSE}
price_chart <- function(data) {
  
  p <- ggplot(data = fast, aes(x=X)) + 
    geom_line(aes(y = midpoint), color = "black") +
    scale_x_continuous(name = "Time") +
    scale_y_continuous(name = "Price") +
    labs(title = "Stock Price (March 2022)")
  
  options(repr.plot.width = 14, repr.plot.height = 8)
  
  return(p)
}
```



```{r, echo = FALSE}
# Plot each stock price over time
aapl_chart <- ggplot(data=aapl, aes(x=X, y=midpoint, group=1)) +
  geom_line() + 
  labs(title = "Apple Stock Price (March 2022)") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Price ($)")

cvx_chart <- ggplot(data=cvx, aes(x=X, y=midpoint, group=1)) +
  geom_line() + 
  labs(title = "Chevron Stock Price (March 2022)") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Price ($)")

fast_chart <- ggplot(data=fast, aes(x=X, y=midpoint, group=1)) +
  geom_line() + 
  labs(title = "Fastenal Stock Price (March 2022)") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Price ($)")

jd_chart <- ggplot(data=jd, aes(x=X, y=midpoint, group=1)) +
  geom_line() + 
  labs(title = "JD.com Stock Price (March 2022)") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Price ($)")

jpm_chart <- ggplot(data=jpm, aes(x=X, y=midpoint, group=1)) +
  geom_line() + 
  labs(title = "JP Morgan Stock Price (March 2022)") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Price ($)")

ms_chart <- ggplot(data=ms, aes(x=X, y=midpoint, group=1)) +
  geom_line() + 
  labs(title = "Morgan Stanley Stock Price (March 2022)") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Price ($)")

spce_chart <- ggplot(data=spce, aes(x=X, y=midpoint, group=1)) +
  geom_line() + 
  labs(title = "Virgin Galactic Stock Price (March 2022)") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Price ($)")

tsla_chart <- ggplot(data=tsla, aes(x=X, y=midpoint, group=1)) +
  geom_line() + 
  labs(title = "Tesla Stock Price (March 2022)") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Price ($)")

wba_chart <- ggplot(data=wba, aes(x=X, y=midpoint, group=1)) +
  geom_line() + 
  labs(title = "Walgreens Stock Price (March 2022)") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Price ($)")

xom_chart <- ggplot(data=xom, aes(x=X, y=midpoint, group=1)) +
  geom_line() + 
  labs(title = "Exxon Mobil Stock Price (March 2022)") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Price ($)")

```


```{r, echo = FALSE}
aapl_chart
```
&nbsp;
```{r, echo = FALSE}
cvx_chart
```
&nbsp;
```{r, echo = FALSE}
fast_chart
```
&nbsp;
```{r, echo = FALSE}
jd_chart
```
&nbsp;
```{r, echo = FALSE}
jpm_chart
```
&nbsp;
```{r, echo = FALSE}
ms_chart
```
&nbsp;
```{r, echo = FALSE}
spce_chart
```
&nbsp;
```{r, echo = FALSE}
tsla_chart
```
&nbsp;
```{r, echo = FALSE}
wba_chart
```
&nbsp;
```{r, echo = FALSE}
xom_chart
```
&nbsp;

\newpage

# Volume
```{r, echo = FALSE}
volume_plot <- function(data) {
  data$vol_ma <- movavg(data$volume, 52, type = "e")
  
  p <- ggplot(data = data, aes(x = X)) + 
    geom_bar(aes(y = volume), stat="identity", linewidth=.1, color = "blue", alpha=.4) +
    geom_line(aes(y = vol_ma), color = "red") +
    scale_x_continuous(name = "Time") +
    scale_y_continuous(name = "Volume") +
    labs(title = "Volume")
  
  options(repr.plot.width = 14, repr.plot.height = 8)
  
  return(p)
}
```



```{r, echo = FALSE}
fast$vol_ma <- movavg(fast$volume, 130, type = "e")
```

```{r, echo = FALSE, warning = FALSE}
fast_vol <- ggplot(data = fast, aes(x = X)) + 
  geom_bar(aes(y = volume), stat="identity", linewidth=.1, color = "blue", alpha=.4) +
  geom_line(aes(y = vol_ma), color = "red") +
  scale_x_continuous(name = "Time") +
  scale_y_continuous(name = "Volume") +
  labs(title = "Volume")
```


## Fastenal
```{r, echo = FALSE, warning = FALSE}
fast_vol
```
&nbsp;
&nbsp;

## Walgreens
```{r, echo = FALSE}
volume_plot(wba)
```
&nbsp;
&nbsp;

## Apple
```{r, echo = FALSE}
volume_plot(aapl)
```
&nbsp;
&nbsp;

## Morgan Stanley
```{r, echo = FALSE}
volume_plot(ms)
```
&nbsp;
&nbsp;

## Chevron
```{r, echo = FALSE}
volume_plot(cvx)
```
&nbsp;
&nbsp;

## JP Morgan
```{r, echo = FALSE, warning = FALSE}
volume_plot(jpm)
```
&nbsp;
&nbsp;

## Exxon Mobil
```{r, echo = FALSE, warning = FALSE}
volume_plot(xom)
```
&nbsp;
&nbsp;

## Tesla
```{r, echo = FALSE, warning = FALSE}
volume_plot(tsla)
```
&nbsp;
&nbsp;

## JD.com
```{r, echo = FALSE, warning = FALSE}
volume_plot(jd)
```
&nbsp;
&nbsp;

## Virgin Galactic
```{r, echo = FALSE, warning = FALSE}
volume_plot(spce)
```

\newpage

# Technical Indicators
I will explore these 6 indicators:

* Simple moving average (SMA)
* Exponential weighted moving average (EWMA)
* Bollinger Bands (BB)
* Relative strength index (RSI)
* Moving average convergence divergence (MACD)
* On-balance volume


I also considered calculating these following indicators, but there was not enough data to create a meaningful plot:

* Average directional index
* Aroon indicator
* Stochastic oscillator
* Accumulation/distribution line


\newpage

# Simple Moving Average (SMA)
The simple moving average can be used to find support and resistance

```{r, echo = FALSE}
sma_plot <- function(data) {
  data$ma_daily <- movavg(data$midpoint, 26, type = "s")
  data$ma_twoday <- movavg(data$midpoint, 52, type = "s")
  data$ma_weekly <- movavg(data$midpoint, 130, type = "s")
  
  
  p <- ggplot(data = data, aes(x = X)) + 
    
    geom_line(aes(y = midpoint), color = "steelblue") +
    geom_line(aes(y = ma_daily), color = "orange") +
    geom_line(aes(y = ma_twoday), color = "red") +
    geom_line(aes(y = ma_weekly), color = "black") + 
    labs(title = "Moving Averages (March 2022)") +
    scale_x_continuous(name = "Time") +
    scale_y_continuous(name = "Price ($)")
  
  options(repr.plot.width = 14, repr.plot.height = 8)
  
  return(p)
}
```

## Fastenal
```{r, echo = FALSE}
sma_plot(fast)
```
&nbsp;
&nbsp;

## Walgreens
```{r, echo = FALSE}
sma_plot(wba)
```
&nbsp;
&nbsp;

## Apple
```{r, echo = FALSE}
sma_plot(aapl)
```
&nbsp;
&nbsp;

## Morgan Stanley
```{r, echo = FALSE}
sma_plot(ms)
```
&nbsp;
&nbsp;

## Chevron
```{r, echo = FALSE}
sma_plot(cvx)
```
&nbsp;
&nbsp;

## JP Morgan
```{r, echo = FALSE}
sma_plot(jpm)
```
&nbsp;
&nbsp;

## Exxon Mobil
```{r, echo = FALSE}
sma_plot(xom)
```
&nbsp;
&nbsp;

## Tesla
```{r, echo = FALSE}
sma_plot(tsla)
```
&nbsp;
&nbsp;

## JD.com
```{r, echo = FALSE}
sma_plot(jd)
```

\newpage
# Exponential Weighted Moving Average (EWMA)

The exponential weighted moving average is used as a measure of volatility through historical predictions from past pricing data and implied predictions from market conditions.

```{r, echo = FALSE}
ewma_plot <- function(data) {
  data$ewma <- movavg(data$midpoint, 26, type = "e")
  data$ma_daily <- movavg(data$midpoint, 26, type = "s")
  
  p <- ggplot(data = data, aes(x = X)) + 
    geom_line(aes(y = midpoint), color = "steelblue") +
    geom_line(aes(y = ma_daily), color = "orange") +
    geom_line(aes(y = ewma), color = "black") +
    labs(title = "Exponential Weighted Moving Average (March 2022)") +
    scale_x_continuous(name = "Time") +
    scale_y_continuous(name = "Price ($)")
  
  options(repr.plot.width = 14, repr.plot.height = 8)
  
  return(p)
}
```


## Fastenal
```{r, echo = FALSE, warning = FALSE}
ewma_plot(fast)
```
&nbsp;
&nbsp;

## Walgreens
```{r, echo = FALSE, warning = FALSE}
ewma_plot(wba)
```
&nbsp;
&nbsp;

## Apple
```{r, echo = FALSE, warning = FALSE}
ewma_plot(aapl)
```
&nbsp;
&nbsp;

## Morgan Stanley
```{r, echo = FALSE, warning = FALSE}
ewma_plot(ms)
```
&nbsp;
&nbsp;

## Chevron
```{r, echo = FALSE, warning = FALSE}
ewma_plot(cvx)
```
&nbsp;
&nbsp;

## JP Morgan
```{r, echo = FALSE, warning = FALSE}
ewma_plot(jpm)
```
&nbsp;
&nbsp;

## Exxon Mobil
```{r, echo = FALSE, warning = FALSE}
ewma_plot(xom)
```
&nbsp;
&nbsp;

## Tesla
```{r, echo = FALSE, warning = FALSE}
ewma_plot(tsla)
```
&nbsp;
&nbsp;

## JD.com
```{r, echo = FALSE, warning = FALSE}
ewma_plot(jd)
```
&nbsp;
&nbsp;

## Virgin Galactic
```{r, echo = FALSE, warning = FALSE}
ewma_plot(spce)
```


\newpage


```{r, include = FALSE, echo = FALSE}
# Returns a data frame including the high, low, and close prices for each day.
hlc_plot <- function(data) {
  prices <- data$midpoint
  
  # Initialize each column
  high_prices <- list()
  low_prices <- list()
  close_prices <- list()
  
  
  # Loop through each day
  for (i in 1:23) {
    # Calculate the indices for that day's prices
    start_idx <- (i-1)*26 + 1
    end_idx <- i*26
    
    # Get that day's prices
    day_prices <- prices[start_idx:end_idx]
    
    # Get the high, low, and close prices for that day
    high <- max(day_prices)
    low <- min(day_prices)
    close <- day_prices[length(day_prices)]
    
    # Append the prices to the appropriate lists
    high_prices[[i]] <- high
    low_prices[[i]] <- low
    close_prices[[i]] <- close
  }

  
  # Concatenate columns
  hlc <- data.frame(high=unlist(high_prices), low=unlist(low_prices), close=unlist(close_prices))
  hlc$x <- 1:23
  
  p <- ggplot(data = hlc, aes(x = x)) + 
    
    geom_segment(aes(y = high, yend = low, xend = x, color = "HLC")) +
    
    geom_point(aes(y = close, color = "Close"), size = 3) +
    
    scale_color_manual(name = "Price", values = c("HLC" = "black", "Close" = "red")) +
    
    labs(title = "High/Low/Close Prices (March 2022)") +
    scale_x_continuous(name = "Time") +
    scale_y_continuous(name = "Price ($)")
  
  options(repr.plot.width = 14, repr.plot.height = 8)
  
  return(p)
}
```


## Fastenal
```{r, echo = FALSE}
fast_hlc <- hlc_plot(fast)
fast_hlc
```

&nbsp;
&nbsp;

## Walgreens
```{r, echo = FALSE}
wba_hlc <- hlc_plot(wba)
wba_hlc
```

&nbsp;
&nbsp;

## Apple
```{r, echo = FALSE}
aapl_hlc <- hlc_plot(aapl)
aapl_hlc
```

&nbsp;
&nbsp;

## Morgan Stanley
```{r, echo = FALSE}
ms_hlc <- hlc_plot(ms)
ms_hlc
```

&nbsp;
&nbsp;

## Chevron
```{r, echo = FALSE}
cvx_hlc <- hlc_plot(cvx)
cvx_hlc
```

&nbsp;
&nbsp;

## JP Morgan
```{r, echo = FALSE}
jpm_hlc <- hlc_plot(jpm)
jpm_hlc
```

&nbsp;
&nbsp;

## Exxon Mobil
```{r, echo = FALSE}
xom_hlc <- hlc_plot(xom)
xom_hlc
```

&nbsp;
&nbsp;

## Tesla
```{r, echo = FALSE}
tsla_hlc <- hlc_plot(tsla)
tsla_hlc
```

&nbsp;
&nbsp;

## JD.com
```{r, echo = FALSE}
jd_hlc <- hlc_plot(jd)
jd_hlc
```

&nbsp;
&nbsp;

## Virgin Galactic
```{r, echo = FALSE}
spce_hlc <- hlc_plot(spce)
spce_hlc 
```






\newpage

# Bollinger Bands (BB)
Bollinger bands consist of the middle band (SMA) and the upper and lower bands, which are 2 standard deviations above and below the SMA, respectively.

```{r, echo = FALSE}
bb_plot <- function(data) {
  data$ma_daily <- movavg(data$midpoint, 26, type = "s")
  data$ma_twoday <- movavg(data$midpoint, 52, type = "s")
  data$ma_weekly <- movavg(data$midpoint, 130, type = "s")
  
  # Calculate one standard deviation of differences between current price and daily moving average
  data$sd <- sd(data$midpoint - data$ma_daily)
  # Calculate upper and lower Bollinger bands
  data$upperBB <- data$ma_daily + 2 * data$sd
  data$lowerBB <- data$ma_daily - 2 * data$sd
  
  
  p <- ggplot(data = data, aes(x = X)) + 
    geom_line(aes(y = upperBB), color = "blue") +
    geom_line(aes(y = ma_daily), color = "black") +
    
    geom_line(aes(y = midpoint), color = "steelblue") +
    geom_line(aes(y = lowerBB), color = "red") +
    scale_x_continuous(name = "Time") +
    scale_y_continuous(name = "Price ($)") + labs(title = "Bollinger Bands")
  
  options(repr.plot.width = 14, repr.plot.height = 8)
  
  return(p)
}
```

## Fastenal
```{r, echo = FALSE}
bb_plot(fast)
```
&nbsp;
&nbsp;

## Walgreens
```{r, echo = FALSE}
bb_plot(wba)
```
&nbsp;
&nbsp;

## Apple
```{r, echo = FALSE}
bb_plot(aapl)
```
&nbsp;
&nbsp;

## Morgan Stanley
```{r, echo = FALSE}
bb_plot(ms)
```
&nbsp;
&nbsp;

## Chevron
```{r, echo = FALSE}
bb_plot(cvx)
```
&nbsp;
&nbsp;

## JP Morgan
```{r, echo = FALSE}
bb_plot(jpm)
```
&nbsp;
&nbsp;

## Exxon Mobil
```{r, echo = FALSE}
bb_plot(xom)
```
&nbsp;
&nbsp;

## Tesla
```{r, echo = FALSE}
bb_plot(tsla)
```
&nbsp;
&nbsp;

## JD.com
```{r, echo = FALSE}
bb_plot(jd)
```
&nbsp;
&nbsp;

## Virgin Galactic
```{r, echo = FALSE}
bb_plot(spce)
```




\newpage


# Relative Strength Index (RSI)
Relative strength index is used to determine momentum of an asset to describe the speed of price changes. Assets are overbought when RSI > 70 and oversold when RSI < 30.

```{r, echo = FALSE}
rsi_plot <- function(data) {
  data$ma_daily <- movavg(data$midpoint, 26, type = "s")
  
  # Calculate relative strength index
  data$rsi <- RSI(data$midpoint, n = 26)
  
  p <- ggplot(data = data, aes(x = X)) + 
    geom_line(aes(y = ma_daily), color = "black") +
    geom_line(aes(y = rsi), color = "orange") + 
    labs(title = "Relative Strength Index (March 2022)") +
    scale_y_continuous(name = "Price ($)", breaks = c(30, 50, 70), limits = c(20,80)) + 
    scale_x_continuous(name = "Relative Strength Index (RSI)")
  
  options(repr.plot.width = 14, repr.plot.height = 8)
  
  return(p)
}
```


## Fastenal 
```{r, echo = FALSE, warning = FALSE}
rsi_plot(fast)
```
&nbsp;
&nbsp;

## Walgreens
```{r, echo = FALSE, warning = FALSE}
rsi_plot(wba)
```
&nbsp;
&nbsp;

## Apple
```{r, echo = FALSE, warning = FALSE}
rsi_plot(aapl)
```
&nbsp;
&nbsp;

## Morgan Stanley
```{r, echo = FALSE, warning = FALSE}
rsi_plot(ms)
```
&nbsp;
&nbsp;

## Chevron
```{r, echo = FALSE, warning = FALSE}
rsi_plot(cvx)
```
&nbsp;
&nbsp;

## JP Morgan
```{r, echo = FALSE, warning = FALSE}
rsi_plot(jpm)
```
&nbsp;
&nbsp;

## Exxon Mobil
```{r, echo = FALSE, warning = FALSE}
rsi_plot(xom)
```
&nbsp;
&nbsp;

## Tesla
```{r, echo = FALSE, warning = FALSE}
rsi_plot(tsla)
```
&nbsp;
&nbsp;

## JD.com
```{r, echo = FALSE, warning = FALSE}
rsi_plot(jd)
```
&nbsp;
&nbsp;

## Virgin Galactic
```{r, echo = FALSE, warning = FALSE}
rsi_plot(spce)
```

\newpage

# Moving Average Convergence/Divergence

```{r, echo = FALSE}
macd_plot <- function(data) {
  data$ma_daily <- movavg(data$midpoint, 26, type = "s")
  data$ma_twoday <- movavg(data$midpoint, 52, type = "s")
  data$ma_weekly <- movavg(data$midpoint, 130, type = "s")
  
  # Calculate the MACD line
  data$macdLine <- data$ma_daily - data$ma_twoday
  
  # Calculate the signal line
  data$signalLine <- movavg(data$macdLine, 9, type = "e")
  
  # Calculate the histogram
  data$histogram <- data$macdLine - data$signalLine
  
  p <- ggplot(data = data, aes(x = X)) + 
    geom_bar(aes(y = histogram), stat="identity", linewidth=.1, color = "blue", alpha=.4) +
    geom_line(aes(y = signalLine), color = "red", linetype = "dashed") +
    geom_line(aes(y = macdLine), color = "steelblue") +
    scale_x_continuous(name = "Time") +
    scale_y_continuous(name = "MACD") +
    labs(title = "Moving Average Convergence/Divergence (March 2022)")
  
  options(repr.plot.width = 14, repr.plot.height = 8)
  
  return(p)
}
```

## Fastenal
```{r, echo = FALSE, warning = FALSE}
macd_plot(fast)
```
&nbsp;
&nbsp;

## Walgreens
```{r, echo = FALSE, warning = FALSE}
macd_plot(wba)
```
&nbsp;
&nbsp;

## Apple
```{r, echo = FALSE, warning = FALSE}
macd_plot(aapl)
```
&nbsp;
&nbsp;

## Morgan Stanley
```{r, echo = FALSE, warning = FALSE}
macd_plot(ms)
```
&nbsp;
&nbsp;

## Chevron
```{r, echo = FALSE, warning = FALSE}
macd_plot(cvx)
```
&nbsp;
&nbsp;

## JP Morgan
```{r, echo = FALSE, warning = FALSE}
macd_plot(jpm)
```
&nbsp;
&nbsp;

## Exxon Mobil
```{r, echo = FALSE, warning = FALSE}
macd_plot(xom)
```
&nbsp;
&nbsp;

## Tesla
```{r, echo = FALSE, warning = FALSE}
macd_plot(tsla)
```
&nbsp;
&nbsp;

## JD.com
```{r, echo = FALSE, warning = FALSE}
macd_plot(jd)
```
&nbsp;
&nbsp;

## Virgin Galactic
```{r, echo = FALSE, warning = FALSE}
macd_plot(spce)
```



\newpage

# On-balance volume
```{r, echo = FALSE}
obv_plot <- function(data) {
  data$obv <- OBV(data$midpoint, data$volume)
  data$obv_ma <- movavg(data$obv, 52, type = "e")
  
  p <- ggplot(data = data, aes(x = data$X)) + 
    geom_bar(aes(y = obv), stat="identity", linewidth=.1, color = "blue", alpha=.4) +
    geom_line(aes(y = obv_ma), color = "red") +
    scale_x_continuous(name = "Time") +
    scale_y_continuous(name = "On Balance Volume") +
    labs(title = "On-Balance Volume")
  
  options(repr.plot.width = 14, repr.plot.height = 8)
    
  return(p)
}
```

## Fastenal
```{r, echo = FALSE, warning = FALSE}
obv_plot(fast)
```
&nbsp;
&nbsp;

## Walgreens
```{r, echo = FALSE, warning = FALSE}
obv_plot(wba)
```
&nbsp;
&nbsp;

## Apple
```{r, echo = FALSE, warning = FALSE}
obv_plot(aapl)
```
&nbsp;
&nbsp;

## Morgan Stanley
```{r, echo = FALSE, warning = FALSE}
obv_plot(ms)
```
&nbsp;
&nbsp;

## Chevron
```{r, echo = FALSE, warning = FALSE}
obv_plot(cvx)
```
&nbsp;
&nbsp;

## JP Morgan
```{r, echo = FALSE, warning = FALSE}
obv_plot(jpm)
```
&nbsp;
&nbsp;

## Exxon Mobil
```{r, echo = FALSE, warning = FALSE}
obv_plot(xom)
```
&nbsp;
&nbsp;

## Tesla
```{r, echo = FALSE, warning = FALSE}
obv_plot(tsla)
```
&nbsp;
&nbsp;

## JD.com
```{r, echo = FALSE, warning = FALSE}
obv_plot(jd)
```
&nbsp;
&nbsp;

## Virgin Galactic
```{r, echo = FALSE, warning = FALSE}
obv_plot(spce)
```


\newpage





